---
title: "VEXP Baby Preprocessing"
author: "Felicia Zhang"
date: '2017-08-23'
output: html_document
---

```{r}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(RColorBrewer)
library(lmerTest)
library(boot)

# 4 counterbalancing orders:
# 1. L=pattern, R=random, L/pattern side first
# 2. L=pattern, R=random, R/random side first
# 3. L=random, R=pattern, L/random side first
# 4. L=random, R=pattern, R/pattern side first

# imgseq = 1 & 2 = left, 3 & 4 = right

# side = 1 = left, 2 = right

# pattern = 0 = random, 1 = pattern, 2 = training

# trial (old) = image on 1000ms, ISI 1200ms, total = 2200ms
# trial (new) = ISI 1200ms, image 1000ms, total = 2200ms

# import pilot data
raw <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/VExP/V1/data/VEXPV1_1-6.csv")

#relabel "condition" column as "counterbalance"
colnames(raw)[colnames(raw)=="condition"] <- "counterbalance"

#remove unuseful columns
raw$LEFT_GAZE_X <- NULL
raw$LEFT_GAZE_Y <- NULL
raw$LEFT_PUPIL_SIZE <- NULL
raw$LEFT_IN_BLINK <- NULL
raw$RIGHT_IN_BLINK <- NULL
raw$SAMPLE_INDEX <- NULL
```

CHANGE FROM V1 after meeting with Lauren:
- go with conservative method
- calculate baseline an additional way: using when babies are looking at image during the training

```{r}
# Make a copy of original 
poo <- subset(raw, TRIAL_INDEX < 93) 

# Class conversions
poo$RIGHT_PUPIL_SIZE <- as.numeric(as.character(poo$RIGHT_PUPIL_SIZE))
poo$RIGHT_GAZE_X <- as.numeric(as.character(poo$RIGHT_GAZE_X))
poo$RIGHT_GAZE_Y <- as.numeric(as.character(poo$RIGHT_GAZE_Y))
summary(poo)

# Warnings appear bc of converting . to NA, which is correct
length(which(raw$RIGHT_PUPIL_SIZE=="."))
length(which(is.na(poo$RIGHT_PUPIL_SIZE)))

# Assigning each subject a number for subID so it's easier to index 
poo$subID <- 0
subs <- unique(poo$RECORDING_SESSION_LABEL)

for (i in 1:length(subs)){
  poo$subID[poo$RECORDING_SESSION_LABEL == subs[i]] <- i
}

unique(poo$subID)

# Standardize time (don't change this TIMECODE code for this experiment it messes up the trial_index)
subs <- unique(poo$subID)

for (j in 1:length(subs)) {
  trials <- unique(poo$TRIAL_INDEX[poo$subID == subs[j]])
  print(subs[j])
  for (i in 1:length(trials)) {
    #gets the timestamp for a trial for a subject
    times = poo$TIMESTAMP[poo$subID == subs[j] & poo$TRIAL_INDEX == trials[i]] 
    start = min(times) #finds the smallest timestamp
    poo$TIMECODE[poo$subID == subs[j] & poo$TRIAL_INDEX == trials[i]] = poo$TIMESTAMP[poo$subID == subs[j] & poo$TRIAL_INDEX == trials[i]] - start
  }}

# For trial 1, only keep the last 2200ms, relabel the other portion as trial 0
subs <- unique(poo$subID)
for (j in 1:length(subs)){
  z <- max(poo$TIMECODE[poo$TRIAL_INDEX==1 & poo$subID == subs[j]])
  zz <- z-2200
  poo$TRIAL_INDEX[poo$subID == subs[j] & poo$TRIAL_INDEX==1 & poo$TIMECODE < zz] <- 0
}

# Recode trial so that each trial is 1200ms ISI -> 1000ms image 
poo$TRIAL_INDEX_RECODE <- 99
for (j in 1:length(subs)) {
  trials <- unique(poo$TRIAL_INDEX[poo$subID == subs[j]])
  trials <- sort(trials)
  print(subs[j])
  for (i in 2:length(trials)) { #starting at trial 1 instead of 0
    #which row is last sample from trial x-1 
    z <- max(which(poo$TRIAL_INDEX==trials[i-1] & poo$subID== subs[j]))
    #which row is 600 rows/1200ms before that
    start <- z-599 #start of new trial
    #which row is first sample from trial x 
    zz <- min(which(poo$TRIAL_INDEX==trials[i] & poo$subID== subs[j]))
    #which row is 500 rows/1000ms after that
    end <- zz+499 #end of new trial
    poo$TRIAL_INDEX_RECODE[start:end] <- trials[i]
    }
  }

# Remove all of the 99 
poo <- subset(poo, TRIAL_INDEX_RECODE !=99)

# Recode Timecode, but can't use TIMESTAMP anymore bc it messes up the timing
poo$TIMECODE_RECODE <- rep(seq(0,2198, by =2), times = 92*(length(subs)))

# Add in trial information
poo$trial <- 1 #picture
poo$trial[poo$TIMECODE_RECODE < 1201] <- 0

# Have to recode imgseq and side because recoding the trial messed it up
for (j in 1:length(subs)) {
  trials <- unique(poo$TRIAL_INDEX_RECODE[poo$subID == subs[j]])
  print(subs[j])
  for (i in 1:length(trials)) {
    #replace the imgseq and side information for trial==0, with trial==1
    poo$imgseq[poo$subID == subs[j] & poo$TRIAL_INDEX_RECODE==trials[i] & poo$trial==0] <- poo$imgseq[poo$subID == subs[j] & poo$TRIAL_INDEX_RECODE==trials[i] & poo$trial==1]
    poo$side[poo$subID == subs[j] & poo$TRIAL_INDEX_RECODE==trials[i] & poo$trial==0] <- poo$side[poo$subID == subs[j] & poo$TRIAL_INDEX_RECODE==trials[i] & poo$trial==1]
  }
}

# Drop unused columns
poo$TRIAL_INDEX <- NULL
poo$TIMECODE <- NULL

# Check hertz recorded at 
for (i in 1:length(unique(poo$subID))) {
blah <- subset(poo, subID == subs[i])
print(i)
print(head(blah$TIMECODE_RECODE))
}
# Conclusion: All were recorded at 500 Hz

# Data reduction, changing 500 Hz to 250 Hz
i <- max(poo$TIMECODE_RECODE)
ii <- seq(2, i, by=4 )
poo <- poo[ !poo$TIMECODE_RECODE %in% ii, ]

# Double check it's at 250 Hz
for (i in 1:length(unique(poo$subID))) {
blah <- subset(poo, subID == subs[i])
print(i)
print(head(blah$TIMECODE_RECODE))
}

# Fill in gaps of blinks
#The duration of a blink is on average 100-150 milliseconds according to UCL researcher (conservative)
#between 100-400ms according to the Harvard Database of Useful Biological Numbers (liberal)

# converts data.frame to data.table, faster to manipulate with large data
poo <- data.table(poo) 

# creates column called 'orig' with row index
poo <- poo[, orig := .I] 

#create empty DF
yoo <- poo[FALSE,]
yoo$rleLength <- NA

# for each subject, create column called rleLength that counts consecutive filled or NA values (to figure out how long NA values are)
for (i in 1:length(subs)) { 
  poo2 <- subset(poo, subID==subs[i])
  poo2 <- poo2[, rleLength := {rr <- rle(is.na(poo2$RIGHT_PUPIL_SIZE)); rep(rr$length, rr$length)}]
  #create column rleLength that counts consecutive filled or NA values (figure out how long NA values are)
  yoo <- rbind(yoo,poo2)
}

# copy to poo DF
poo <- yoo

# Only fill in NA gaps with length < 100 (100 samples = 400ms) going liberal, using linear interpolation na.approx. If you want cubic spline interpolation, use na.spline
poo$RIGHT_PUPIL_SIZE <- with(poo, ifelse(rleLength < 101, na.approx(RIGHT_PUPIL_SIZE), RIGHT_PUPIL_SIZE))

summary(poo$RIGHT_PUPIL_SIZE) 
#RESULT = 33% blank

# Relabel gazes that are off the screen as NA (screen dimensions of screen are 1280 x 1024)
poo[, 2][poo[, 2] < 0] <- NA
poo[, 2][poo[, 2] > 1280] <- NA

# Relabel raw pupil size as NA if the gaze coordinates are NA and it's not a blink. We interpolated some missing RIGHT_PUPIL_SIZE data because it was a blink. So don't want to replace those values with NA.
a <- which(is.na(poo$RIGHT_GAZE_X & poo$rleLength > 100))
poo$RIGHT_PUPIL_SIZE[a] <- NA

# Convert pupil area to diameter for certain participants 
# diameter = 256 * sqrt(area / Pi)
diameter <- function (x) {
  256*sqrt(x/pi)
}

subs <- unique(poo$subID)

for (i in 1:length(subs)){
  summary(poo$RIGHT_PUPIL_SIZE[poo$subID==subs[i]])
  a <- summary(poo$RIGHT_PUPIL_SIZE[poo$subID==subs[i]])
  if (a[4] < 1000){ #meaning it's recorded in area
    start <- min(which(poo$subID==subs[i])) #find start of that participant
    end <- max(which(poo$subID==subs[i])) #find end of that participant
    poo$RIGHT_PUPIL_SIZE[start:end] <- sapply(poo$RIGHT_PUPIL_SIZE[start:end],diameter) 
  }
  }

# Label training vs test trials
poo$phase <- 0 #training
poo$phase[poo$TRIAL_INDEX_RECODE > 12] <- 1 #test

# Label if image appeared on left or right (imgseq = 1 & 2 = left, 3 & 4 = right)
# training phase (0) already has correct side information but not test phase (1)
poo$side[poo$imgseq==1 & poo$phase == 1] <- 1
poo$side[poo$imgseq==2 & poo$phase == 1] <- 1
poo$side[poo$imgseq==3 & poo$phase == 1] <- 2
poo$side[poo$imgseq==4 & poo$phase == 1] <- 2

# Label if condition is random (0) or pattern (1) or training (2)
# 1. L=pattern, R=random, 
# 2. L=pattern, R=random,
# 3. L=random, R=pattern, 
# 4. L=random, R=pattern,

poo$condition[poo$phase==0] <- 2 #training trials are labelled as 2
poo$condition[poo$phase==1 & poo$counterbalance==1 & poo$side==1] <- 1
poo$condition[poo$phase==1 & poo$counterbalance==1 & poo$side==2] <- 0
poo$condition[poo$phase==1 & poo$counterbalance==2 & poo$side==1] <- 1
poo$condition[poo$phase==1 & poo$counterbalance==2 & poo$side==2] <- 0
poo$condition[poo$phase==1 & poo$counterbalance==3 & poo$side==1] <- 0
poo$condition[poo$phase==1 & poo$counterbalance==3 & poo$side==2] <- 1
poo$condition[poo$phase==1 & poo$counterbalance==4 & poo$side==1] <- 0
poo$condition[poo$phase==1 & poo$counterbalance==4 & poo$side==2] <- 1

# BASELINE OPTION A. Use the average pupil size during training trials, when image is on screen to calculate baseline. 
pooA <- subset(poo, TRIAL_INDEX_RECODE >0)
pooA$PUPIL_CORRECTED <- 999

subs <- unique(pooA$subID)
for (j in 1:length(subs)) {
  leftavg <- mean(pooA$RIGHT_PUPIL_SIZE[pooA$subID==subs[j] & pooA$phase==0 & pooA$trial==1 & pooA$side==1], na.rm = TRUE) #average pupil size for a subject, during training, when image is on the left side 
  rightavg <- mean(pooA$RIGHT_PUPIL_SIZE[pooA$subID==subs[j] & pooA$phase==0 & pooA$trial==1 & pooA$side==2], na.rm = TRUE) #average pupil size for a subject, during training, when image is on the right side 
  
  #percent pupil change from baseline for a subject
  pooA$PUPIL_CORRECTED[pooA$subID==subs[j] & pooA$phase==1 & pooA$side==1] <- (pooA$RIGHT_PUPIL_SIZE[pooA$subID==subs[j] & pooA$phase==1 & pooA$side==1] - leftavg) / leftavg
  pooA$PUPIL_CORRECTED[pooA$subID==subs[j] & pooA$phase==1 & pooA$side==2] <- (pooA$RIGHT_PUPIL_SIZE[pooA$subID==subs[j] & pooA$phase==1 & pooA$side==2] - rightavg) / rightavg
  }

#relabel training pupil corrected from 999 to NA
pooA$PUPIL_CORRECTED[pooA$phase==0] <- NA

poo <- pooA
```

For each trial, calculate percent trackloss (AKA NA and gazes that are off screen)
```{r}
# calculate trackloss
trackloss <- group_by(poo, subID, TRIAL_INDEX_RECODE) %>%
  summarise(
    missingdata = length(which(is.na(RIGHT_PUPIL_SIZE))),
    totaldata = n()
  )

trackloss$percentmissing <- trackloss$missingdata / trackloss$totaldata

trackloss$missingdata <- NULL
trackloss$totaldata <- NULL

poo <- merge(poo, trackloss)
```

Code every sample if they're looking at target (conservative)
```{r}
#screen dimensions of screen are 1280 x 1024
#might need to adjust these numbers to make the range larger for babies
leftx1 <- 250
leftx2 <- 500
rightx1 <- 780
rightx2 <- 1030
poo$lookattarget <- 9

poo2 <- poo %>%
mutate(lookattarget = 
ifelse(side ==1 & RIGHT_GAZE_X > leftx1 & RIGHT_GAZE_X < leftx2, 1,
ifelse(side ==1 & RIGHT_GAZE_X > rightx1 & RIGHT_GAZE_X < rightx2, 0, 
ifelse(side ==2 & RIGHT_GAZE_X > rightx1 & RIGHT_GAZE_X < rightx2, 1, 
ifelse(side ==2 & RIGHT_GAZE_X > leftx1 & RIGHT_GAZE_X < leftx2, 0,
ifelse(is.na(RIGHT_GAZE_X), 9, 5 ))))))

poo2$lookattarget[is.na(poo2$lookattarget)] <- 9

#double check it worked
blah <- subset(poo2, lookattarget==1 & side ==1)
ggplot(blah,aes(x=RIGHT_GAZE_X,y=RIGHT_GAZE_Y,color=factor(subID),fill=factor(subID)))+
  geom_point()+
  ggtitle("Left")+
  scale_x_continuous(limits=c(0,1280),breaks=seq(0,1280,200))+
  scale_y_continuous(limits=c(0,1025),breaks=seq(0,1025,100))

blah <- subset(poo2, lookattarget==1 & side ==2)
ggplot(blah,aes(x=RIGHT_GAZE_X,y=RIGHT_GAZE_Y,color=factor(subID),fill=factor(subID)))+
  geom_point()+
  ggtitle("Right")+
  scale_x_continuous(limits=c(0,1280),breaks=seq(0,1280,200))+
  scale_y_continuous(limits=c(0,1025),breaks=seq(0,1025,100))

blah <- subset(poo2, lookattarget==5)
ggplot(blah,aes(x=RIGHT_GAZE_X,y=RIGHT_GAZE_Y,color=factor(subID),fill=factor(subID)))+
  geom_point()+
  ggtitle("whatever")+
  scale_x_continuous(limits=c(0,1280),breaks=seq(0,1280,200))+
  scale_y_continuous(limits=c(0,1025),breaks=seq(0,1025,100))
```

# BASELINE OPTION B. Use the average pupil size during training trials, when image is on screen AND subject is looking at target to calculate baseline. 
```{r}
pooA <- subset(poo2, TRIAL_INDEX_RECODE >0)
pooA$PUPIL_CORRECTED2 <- 999

subs <- unique(pooA$subID)
for (j in 1:length(subs)) {
  leftavg <- mean(pooA$RIGHT_PUPIL_SIZE[pooA$subID==subs[j] & pooA$phase==0 & pooA$trial==1 & pooA$lookattarget==1 & pooA$side==1], na.rm = TRUE) #average pupil size for a subject, during training, when image is on the left side 
  rightavg <- mean(pooA$RIGHT_PUPIL_SIZE[pooA$subID==subs[j] & pooA$phase==0 & pooA$trial==1 & pooA$lookattarget==1 & pooA$side==2], na.rm = TRUE) #average pupil size for a subject, during training, when image is on the right side 
  
  #percent pupil change from baseline for a subject
  pooA$PUPIL_CORRECTED2[pooA$subID==subs[j] & pooA$phase==1 & pooA$side==1] <- (pooA$RIGHT_PUPIL_SIZE[pooA$subID==subs[j] & pooA$phase==1 & pooA$side==1] - leftavg) / leftavg
  pooA$PUPIL_CORRECTED2[pooA$subID==subs[j] & pooA$phase==1 & pooA$side==2] <- (pooA$RIGHT_PUPIL_SIZE[pooA$subID==subs[j] & pooA$phase==1 & pooA$side==2] - rightavg) / rightavg
  }

#relabel training pupil corrected from 999 to NA
pooA$PUPIL_CORRECTED2[pooA$phase==0] <- NA

poo3 <- pooA

# save to computer
write.csv(poo3, "VEXP_1-6_Preprocessed.csv", row.names=TRUE) #save to computer
```

Scatterplot of pupil size per subject using pupil_corrected
```{r}
#replace infinite with NA
is.na(poo3$PUPIL_CORRECTED) <- sapply(poo3$PUPIL_CORRECTED, is.infinite)

#scatterplot of pupil size per subject
pupil.sub <- group_by(poo3, subID, TRIAL_INDEX_RECODE, phase,trial) %>%
  summarise(
    pupilsize=mean(PUPIL_CORRECTED,na.rm = TRUE)
    )

pupil.sub2 <- subset(pupil.sub, trial==1 & phase==1) #only plot pupil when they're looking at image and during test phase

ggplot(pupil.sub2,aes(x=factor(subID),y=pupilsize,fill=factor(TRIAL_INDEX_RECODE),color=factor(TRIAL_INDEX_RECODE)))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+
  ggtitle("Pupil change per subject (no filter)")+
  labs(x = "Subject", y = "Pupil change (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent)
```

Scatterplot of pupil size per subject using pupil_corrected2
```{r}
#replace infinite with NA
is.na(poo3$PUPIL_CORRECTED2) <- sapply(poo3$PUPIL_CORRECTED2, is.infinite)

#scatterplot of pupil size per subject
pupil.sub <- group_by(poo3, subID, TRIAL_INDEX_RECODE, phase,trial) %>%
  summarise(
    pupilsize=mean(PUPIL_CORRECTED2,na.rm = TRUE)
    )

pupil.sub2 <- subset(pupil.sub, trial==1 & phase==1) #only plot pupil when they're looking at image and during test phase

ggplot(pupil.sub2,aes(x=factor(subID),y=pupilsize,fill=factor(TRIAL_INDEX_RECODE),color=factor(TRIAL_INDEX_RECODE)))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+
  ggtitle("Pupil change per subject (no filter)")+
  labs(x = "Subject", y = "Pupil change (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent)
```

look at raw pupil size to see if there's a difference between left or right side
y axis= right pupil size on y, x axis= x coordinate 
```{r}
#(screen dimensions of screen are 1280 x 1024)
goo <- group_by(poo, RECORDING_SESSION_LABEL, RIGHT_GAZE_X) %>%
  summarise(
    meanpupil = mean(RIGHT_PUPIL_SIZE, na.rm = TRUE)
  )

goo2 <- group_by(goo, RIGHT_GAZE_X) %>%
  summarise(
    meanpupil2 = mean(meanpupil, na.rm = TRUE)
  )

ggplot(goo2,aes(x=RIGHT_GAZE_X,y=meanpupil2))+
  geom_point(size=2)+
  ggtitle("Changes in raw pupil size")+
  scale_x_continuous(limits=c(0,1280),breaks=seq(0,1280,250))+
  scale_y_continuous(limits=c(0,8000),breaks=seq(0,8000,500))+
  labs(x = "X coordinate", y = "Average raw pupil size")

```

